### 2021-05-17 chatbot_classification/03.emnlp_2021/experiments.tex
modified:   experiments.tex

\begin{enumerate}
  \item \emph{ITG},  is  a proprietary FAQ dataset from real-world
  chatbot  project,  which is composed of question and answer pairs about online
  English teaching. It contains 3,938 sample questions for 228 class labels, and
  each class label corresponds to a unique answer.

  \item \emph{Amazon-670K}, is a customer product review dataset for
  text  classification  task  from  the  extreme  classification repository. The
  complete  dataset  contains 670,091 class labels, 285,176 training samples and
  150,875   testing   samples   \cite{bhatia2016extreme}.  As  each  sample  may
  correspond  to  multiple  class labels, we keep only the first one. We further
  filter  out the class labels that only associated to training samples within the amount of 5 to 15 to  mimic  the  few-shot chatbot scenario. From them, we sample 250 class
  labels as well as their training samples to form a subset with 2658 samples.

  \item \emph{HWU64}, is an intent detection dataset designed for
  home  robot  scenario \cite{liu2019benchmarking}. It aims at the specific task
  of  capturing  the  intent  for  different  user requests to home robot and
  finding  the corresponding answer. The raw dataset contains 25,716 data points
  for 64 class labels through crowdsourcing.

  \item \emph{CLINC150},  is  a dataset designed for task-oriented
  systems  with  23,700 queries that are short and unstructured for 150 intents,
  in    the    same   style   made   by   real   users   through   crowdsourcing
  \cite{larson2019evaluation}.

  \item \emph{BANKING77}, is an intent detection dataset for bank
  customer  services.  The  raw dataset contains 13,084 data points for 77 class
  labels \cite{casanueva2020efficient}.

  \item \emph{FRAMES}, is a collection of multi-domain dialogues dealing with
hotel bookings. The raw data is consists of 1369 human-human
dialogues with slot filling information. There are 30,522 utterances in total for 21 intents and 49 slots \cite{asri2017frames}.

  \item \emph{ATIS}, is a popular dataset for intent detection of flight reservations with slot filling\cite{tur2010left}. The raw data's training, development and test sets contain 4,478, 500 and 893 utterances, respectively. There are 120 slot labels and 21 intent types for the training set.

\end{enumerate}

@@

\subsection{Baselines}
Our baselines comprise of four styles of systems.

\begin{enumerate}
  \item   
  \emph{Non-pretrained   model  based  classification  system},  which consists  of  a typical CNN based TextCNN \cite{kim2014convolutional}, and a label-embedding based LEAM \cite{wang2018joint}. 
  Regarding TextCNN, the input is from RoBERTa tokenization, and the kernels are set as 1, 2, 3, 4, 5. 
  Regarding LEAM, a literal class label is required, which is available only in HWU64, CLINC150, BANKING77. 
  Thus, for other two datasets, we have to use its class number instead.  
  Empirically, a  non-pretrained  model  based  system  are  not  performing  as  well as a pretrained  models  based in many NLP tasks.
  Our listing these  non-pretrained model based systems here is serving a comprehensive performance comparison on our datasets.

  \item 
  \emph{Pretrained model based classification system}, which consists of BERT \cite{devlin2018bert},  RoBERTa \cite{liu2019roberta},  and  ALBERT  \cite{lan2019albert}  based.  
  These pretrained models  are  practically  proven  to  achieve  outstanding  performances  in classification task and other NLP tasks.

  \item   
  \emph{Pre-trained   model   based   similarity   model}.  
  As RoBERTa is empirically found more effective than other pretrained models  in  the  short  text  classification  task  in  our  experiments, we  choose RoBERTa-large  based implementation.
  In inference,  we  use  an  elastic search to find a set of potential candidate labels for the similarity model, to guarantee a reasonable running time.

  \item 
  \emph{Pre-trained model based joint text classification and NER model}. 
  We choose the work from \cite{chen2019bert}, which utilizes a RoBERTa-large model to jointly train two losses, as our baseline system.
  Our  SFC framework  is also conveniently supportive of extra NER loss that in  stage  1 a fourth task for NER loss is trivially derived  based on the  output states from a pretrained model.

\end{enumerate}

All our pretrained model   baselines  are  fine-tuned  on  our datasets.
Especially, the similarity  model  baseline  and all similarity modules in SFCs use extra Quora  dataset  \cite{iyer2017first}  to enhance system performance. 
This is also one of merits in SFC as it support adopting out-of-domain data in comparison to a classification based model.

Our SFC implementations include three 2-stage SFCs, which uses task 1 and 2 with ablation in Table \ref{tbe:table2} ; one joint-SFC which is trained jointly on all three tasks in Table \ref{tbe:table2}; one joint-SFC with an additional fourth NER task in Table \ref{tbe:addtional ner experiments}.

@@

\begin{table}
  \begin{centering}
    \scalebox{0.58}{
      \begin{tabular}{|c|ccc|ccc|}
        \hline
        \multicolumn{1}{|c|}{\multirow{2}*{\textbf{Models}} }& \multicolumn{3}{c|}{\textbf{FRAMES}}& \multicolumn{3}{c|}{\textbf{ATIS}}\tabularnewline
        \cline{2-7}
        \multicolumn{1}{|c|}{} & $\textbf{10}$ & $\textbf{20}$ & $\textbf{50}$
        & $\textbf{10}$ & $\textbf{20}$ & $\textbf{50}$\tabularnewline
        \hline
        RoBERTa-large & \multirow{2}*{${0.3456}$} & \multirow{2}*{${0.4043}$} & \multirow{2}*{${0.4262}$} & \multirow{2}*{${0.9349}$} & \multirow{2}*{${0.9757}$} & \multirow{2}*{${0.9800}$}\tabularnewline
        (classification) & & & & & & \tabularnewline
        \hline
        RoBERTa-large & \multirow{3}*{${0.3520}$} & \multirow{3}*{${0.4088}$} & \multirow{3}*{${0.4353}$} & \multirow{3}*{${0.9560}$} & \multirow{3}*{${0.9706}$} & \multirow{3}*{$\textbf{0.9832}$}\tabularnewline
        (classification & & & & & & \tabularnewline
        w/ NER) & & & & & & \tabularnewline
        \hline
        Joint-SFC & \multirow{2}*{${0.3843}$} &
        \multirow{2}*{${0.4130}$} & \multirow{2}*{${0.4390}$} &
        \multirow{2}*{${0.9618}$} & \multirow{2}*{${0.9761}$} & 
        \multirow{2}*{${0.9825}$}\tabularnewline
        (w/o NER) & & & & & & \tabularnewline
        \hline
        Joint-SFC & \multirow{2}*{$\textbf{0.3925}$} &
        \multirow{2}*{$\textbf{0.4420}$} & \multirow{2}*{$\textbf{0.4456}$} &
        \multirow{2}*{$\textbf{0.9639}$} & \multirow{2}*{$\textbf{0.9784}$} & 
        \multirow{2}*{${0.9826}$}\tabularnewline
        (w/ NER) & & & & & & \tabularnewline
        \hline
      \end{tabular}
    }

  \end{centering}
  \caption{
    F1 scores for joint sentence classification and NER training. 
    Regarding both FRAMES and ATIS dataset, we set up various few-shot settings (10/20/50 samples per intent) while fixing the original test set.
  }
  \label{tbe:addtional ner experiments}
\end{table}

>>>>

\emph{ITG}, is a proprietary FAQ dataset from real-world
chatbot project, which is composed of question and answer pairs about online
English teaching. It contains 3,938 sample questions for 228 class labels, and
each class label corresponds to a unique answer.

\emph{Amazon-670K}, is a customer product review dataset for
text classification task from the extreme classification repository. The
complete dataset contains 670,091 class labels, 285,176 training samples and
150,875 testing samples \cite{bhatia2016extreme}. As each sample may
correspond to multiple class labels, we keep only the first one. We further
filter out the class labels that only associated to training samples within the amount of 5 to 15 to mimic the few-shot chatbot scenario. From them, we sample 250 class
labels as well as their training samples to form a subset with 2658 samples.

\emph{HWU64}, is an intent detection dataset designed for
home robot scenario \cite{liu2019benchmarking}. It aims at the specific task
of capturing the intent for different user requests to home robot and
finding the corresponding answer. The raw dataset contains 25,716 data points
for 64 class labels through crowdsourcing.

\emph{CLINC150}, is a dataset designed for task-oriented
systems with 23,700 queries that are short and unstructured for 150 intents,
in the same style made by real users through crowdsourcing
\cite{larson2019evaluation}.

\emph{BANKING77}, is an intent detection dataset for bank
customer services. The raw dataset contains 13,084 data points for 77 class
labels \cite{casanueva2020efficient}.

\emph{FRAMES}, is a collection of multi-domain dialogues dealing with
hotel bookings. The raw data is consists of 1369 human-human
dialogues with slot filling information. There are 30,522 utterances in total for 21 intents and 49 slots \cite{asri2017frames}.

\emph{ATIS}, is a popular dataset for intent detection of flight reservations with slot filling\cite{tur2010left}. The raw data's training, development and test sets contain 4,478, 500 and 893 utterances, respectively. There are 120 slot labels and 21 intent types for the training set.

@@

\subsection{Baselines}
Our baselines comprise of \emph{four} styles of systems.

The first one, \emph{Non-pretrained model based classification system}, which consists of a typical CNN based TextCNN \cite{kim2014convolutional}, and a label-embedding based LEAM \cite{wang2018joint}. 
Regarding TextCNN, the input is from RoBERTa tokenization, and the kernels are set as 1, 2, 3, 4, 5. 
Regarding LEAM, a literal class label is required, which is available only in HWU64, CLINC150, BANKING77. 
Thus, for other two datasets, we have to use its class number instead. 
Empirically, a non-pretrained model based system are not performing as well as a pretrained models based in many NLP tasks.
Our listing these non-pretrained model based systems here is serving a comprehensive performance comparison on our datasets.

The second one, \emph{pretrained model based classification system}, which consists of BERT \cite{devlin2018bert}, RoBERTa \cite{liu2019roberta}, and ALBERT \cite{lan2019albert} based. 
These pretrained models are practically proven to achieve outstanding performances in classification task and other NLP tasks.

The third one, \emph{pretrained model based similarity model}. 
As RoBERTa is empirically found more effective than other pretrained models in the short text classification task in our experiments, we choose RoBERTa-large based implementation.
In inference, we use an elastic search to find a set of potential candidate labels for the similarity model, to guarantee a reasonable running time.

The fouth one, \emph{pretrained model based joint text classification and NER model}. 
We choose the work from \cite{chen2019bert} as our baseline system, which utilizes a strong RoBERTa-large model to jointly train two losses.
Our SFC framework is also conveniently supportive of extra NER loss that in stage 1 a fourth task with a NER loss is trivially derived based on the output states from a pretrained model.

All pretrained model baselines are fine-tuned on our datasets.
Especially, the similarity model baseline and all similarity layers in SFCs use extra Quora dataset \cite{iyer2017first} to enhance system performance. 
This is also one of merits in SFC, as it support adopting out-of-domain data in comparison to a classification based model.

Our SFC implementations include three 2-stage SFCs using task 1 and 2 with ablation in Table \ref{tbe:table2}; one joint-SFC trained on all three tasks in Table \ref{tbe:table2}; one joint-SFC with an additional fourth NER task in Table \ref{tbe:addtional ner experiments}.

@@

\begin{table}
  \begin{centering}
    \scalebox{0.65}{
      \begin{tabular}{|c|ccc|ccc|}
        \hline
        \multicolumn{1}{|c|}{\multirow{2}*{\textbf{Models}} }& \multicolumn{3}{c|}{\textbf{FRAMES}}& \multicolumn{3}{c|}{\textbf{ATIS}}\tabularnewline
        \cline{2-7}
        \multicolumn{1}{|c|}{} & $\textbf{10}$ & $\textbf{20}$ & $\textbf{50}$
        & $\textbf{10}$ & $\textbf{20}$ & $\textbf{50}$\tabularnewline
        \hline
        RoBERTa-large & \multirow{2}*{${0.3456}$} & \multirow{2}*{${0.4043}$} & \multirow{2}*{${0.4262}$} & \multirow{2}*{${0.9349}$} & \multirow{2}*{${0.9757}$} & \multirow{2}*{${0.9800}$}\tabularnewline
        (classification) & & & & & & \tabularnewline
        \hline
        RoBERTa-large & \multirow{3}*{${0.3520}$} & \multirow{3}*{${0.4088}$} & \multirow{3}*{${0.4353}$} & \multirow{3}*{${0.9560}$} & \multirow{3}*{${0.9706}$} & \multirow{3}*{$\textbf{0.9832}$}\tabularnewline
        (classification & & & & & & \tabularnewline
        w/ NER) & & & & & & \tabularnewline
        \hline
        Joint-SFC & \multirow{2}*{${0.3843}$} &
        \multirow{2}*{${0.4130}$} & \multirow{2}*{${0.4390}$} &
        \multirow{2}*{${0.9618}$} & \multirow{2}*{${0.9761}$} & 
        \multirow{2}*{${0.9825}$}\tabularnewline
        (w/o NER) & & & & & & \tabularnewline
        \hline
        Joint-SFC & \multirow{2}*{$\textbf{0.3925}$} &
        \multirow{2}*{$\textbf{0.4420}$} & \multirow{2}*{$\textbf{0.4456}$} &
        \multirow{2}*{$\textbf{0.9639}$} & \multirow{2}*{$\textbf{0.9784}$} & 
        \multirow{2}*{${0.9826}$}\tabularnewline
        (w/ NER) & & & & & & \tabularnewline
        \hline
      \end{tabular}
    }
  \end{centering}

  \caption{
    F1 scores for joint sentence classification and NER training. 
    We iterate various sample number per intent and test on original test set.
  }
  \label{tbe:addtional ner experiments}
\end{table}
